\chapter{Lecture 7}

\section{Quantum BV in Finite Dimensions}

In this section we start out journey towards the quantization of BV theories.
Recall that out goal is to provide a \textbf{homological approach} to compute integrals of the form
\begin{equation*}
  \int_{\phi \in \Fcal} \euler^{- \frac{S}{\hbar}} \DD \phi.
\end{equation*}
We will introduce the quantum BV complex as a generalized \textbf{divergence complex}.
In finite dimensions this is an obscured version of the de Rham complex, where we have the usual homological approach to integration.

For this chapter we return to the finite-dimensional case, which corresponds to the case where spacetime is a point $M = \text{pt}$. Consider:
\begin{enumerate}[i)]
  \item a $n$-dimensional \textbf{graded} vector space $V = \sum_{n \in \Zbb} V_n$ of \textbf{fields};
  \item a $-1$-\textbf{shifted symplectic pairing} $\langle \cdot, \cdot \rangle \colon V \otimes V \to \Rbb$;
  \item an \textbf{action} $S \in \Oscr(V)$ such that
    \begin{equation*}
      \{ S, S \} =  0, \qquad \substack{\text{classical master} \\ \text{equation (CME)}}
    \end{equation*}
    where $\{ \cdot, \cdot \} \colon \Oscr(V) \otimes \Oscr(V) \rightarrow \Oscr(V)$ is the $+1$-\textbf{shifted Poisson bracket} induced by the symplectic pairing.
\end{enumerate}
Such a setup makes $\bigl( \Oscr(V), \{ \cdot, \cdot \} \bigr)$ into a cochain complex such that
\begin{equation*}
  \Hrm^0 \Oscr(V) \cong \Oscr( \Crit (S)).
\end{equation*}

Passing to the derived critical locus, we have seen that functions on $\dCrit(S)$ form a commutative dg algebra
\begin{equation*}
  \Oscr \bigl(\dCrit(S) \bigr) = \bigl( \PV^{\bullet} (V), -\iota_{\drm S} \bigr)
\end{equation*}
which we call the \textbf{classical BV complex}. Passing to the quantum version amounts to deforming this complex by changing the differential.

\section{Integration in Finite Dimensions}

Fixing a nonvanishing top form $\mu \in \Omega^{n}(V)$ defines a map
\begin{align*}
  \int_V \colon \Oscr(V)
  &\longrightarrow \Rbb \\
  f
  &\longmapsto \int_V f \mu
\end{align*}
where we make the necessary assumptions on $\Oscr$ such that $f$ is integrable with respect to $\mu$.
This map depends only on \textbf{cohomological data}. Explicitly, we have that
\begin{equation*}
  \int_M f \mu = \frac{\bigl[f \mu\bigr]}{\bigl[\mu\bigr]}
\end{equation*}
where $[\cdot]$ denotes the cohomology class in $\Hrm_{\text{dR}} (V)$.
Note that the denominator is just a normalizing factor.
If we pick $\mu \in \Omega^n(V)$ such that $\smallint_V \mu = 1$, computing the integral of $f$ with respect to $\mu$ boils down to computing a class in cohomology
\begin{equation*}
  \int_V f \mu = \bigl[f \mu\bigr].
\end{equation*}

The pairing by integration with $\mu$ is nondegenerate so it defines an isomorphism $\Oscr(V) \to \Omega^n(V)$ which we can extends to an isomorphism of complexes
\begin{align*}
  m_\mu \colon \PV^{-k} (V) 
  &\longrightarrow \Omega^{n - k} (V) \\
  X
  &\longmapsto \iota_X \mu.
\end{align*}

\begin{example}
  In coordinates, let $\mu = \drm x^1 \wedge \dots \wedge \drm x^n$ and $X = f \frac{\partial}{\partial x^{j_1}} \wedge \dots \wedge \frac{\partial}{\partial x^{j_k}}$. Then
  \begin{align*}
    m_{\mu} (X)
    &= f m_{\mu} \biggl( \frac{\partial}{\partial x^{j_1}} \wedge \dots \wedge \frac{\partial}{\partial x^{j_k}} \biggr) \\
    &= \sigma f \drm x^1 \dots \drm \hat{x}^{j_i} \dots \drm \hat{x}^{j_k} \dots \drm x^n
  \end{align*}
  where the terms $\drm \hat{x}^{j_i}$ are omitted, and $\sigma = \pm 1$ is such that
  \begin{equation*}
    \sigma \drm x^1 \dots \drm x^n
    = \drm x^{j_1} \dots \drm x^{j_k} \wedge \drm x^1 \dots \drm x^n.
  \end{equation*}
\end{example}

The \textbf{divergence operator} on $\PV^{\bullet}(V)$
\begin{equation*}
  \divergence_\mu = m_\mu^{-1} \drm m_\mu
\end{equation*}
is obtained by pulling back the de Rham differential on $\Omega^{\bullet}$ using $\mu$.
\begin{equation*}
  \begin{tikzcd}[sep=large]
    \dots 
    \arrow[r] &
    \PV^{-2}(V)
    \arrow[r, "\divergence_\mu"] \arrow[d, "m_\mu"] &
    \PV^{-1}(V)
    \arrow[r, "\divergence_\mu"] \arrow[d, "m_\mu"] &
    \Oscr(V)
    \arrow[d, "m_\mu"] \\
    \dots \arrow[r] &
    \Omega^{n-2}(V)
    \arrow[r, "\drm"] &
    \Omega^{n-1}(V)
    \arrow[r, "\drm"] &
    \Omega^{n}(V)
  \end{tikzcd}
\end{equation*}

Because it admits this definition in the finite-dimensional case, we say that the divergence complex is an \textit{obscured} version of the usual de Rham complex.
At this point, one might wonder: why do we not just use the de Rham complex to begin with?
The point is that, unlike the de Rham complex, the divergence complex generalizes to the infinite-dimensional case.

Recall how before we recovered the space of functions on the critical locus $\Crit(S)$ from $\PV^{\bullet}$ by passing to cohomology in degree $0$.
This crucial information is encoded in the de Rham complex in degree $n$, where top forms live.
In infinite dimensions, this data escapes as the de Rham complex ceases to be bounded above.
However, it still resides in degree $0$ in the divergence complex.
In this sense, the natural approach in quantum field theory is to generalize the divergence operator to the infinite-dimensional case.

\begin{example}
  Let $V = \Rbb$ and $\mu_\text{Leb}$ be the Lebesgue measure. A simple computation recovers the usual divergence operator
  \begin{align*}
    \divergence_\text{Leb} \biggl( f \frac{\partial}{\partial  x} \biggr)
    &= m_\mu^{-1} \drm m_\mu \biggl( f \frac{\partial}{\partial x} \biggr) \\
    &= m_\mu^{-1} \bigl( \drm f\bigr) \\
    &= m_\mu^{-1} \biggl( \frac{\partial f}{\partial x} \mu \biggr) \\
    &= \frac{\partial f}{\partial x}.
  \end{align*}
  If we write the generator of the vector fields as $\xi = \frac{\partial}{\partial x}$ then
  \begin{equation*}
    \divergence_\text{Leb} = \frac{\partial}{\partial x} \frac{\partial}{\partial \xi} = \bv
  \end{equation*}
  takes the form of the usual BV Laplacian.
  It is straightforward to generalize to the $n$-dimensional case
  \begin{equation*}
    \divergence_{\text{Leb}} = \bv
    = \sum_{i = 1} \frac{\partial}{\partial x^i} \frac{\partial}{\partial \xi^i}.
  \end{equation*}
\end{example}

\begin{example}
  Consider again $V = \Rbb$ but let $\mu_S$ be a Gaussian measure of the form
  \begin{equation*}
    \mu_S = \euler^{-\frac{S}{\hbar}} \mu_\text{Leb}.
  \end{equation*}
  In this case, we see that
  \begin{align*}
    \divergence_S 
    &= m_{\mu_S}^{-1} \drm m_{\mu_S} \biggl( f \frac{\partial}{\partial x} \biggr) \\
    &= m_{\mu_S}^{-1} \drm \Bigl( f \euler^{-\frac{S}{\hbar}} \Bigr) \\
    &= m_{\mu_S}^{-1} \biggl( \frac{\partial f}{\partial  x} \euler^{-\frac{S}{\hbar}} \mu_\text{Leb}
    - \frac{1}{\hbar} \frac{\partial S}{\partial x} f \euler^{-\frac{S}{\hbar}} \mu_\text{Leb} \biggr) \\
    &= \frac{\partial f}{\partial  x} - \frac{1}{\hbar} \frac{\partial S}{\partial  x} f.
  \end{align*}
  from which we conclude that
  \begin{equation*}
    \divergence_S = - \frac{1}{\hbar} \iota_{\drm S} + \bv.
  \end{equation*}
  If $\hbar \neq 0$ (and is not formal) we can multiply by $\hbar$ to obtain a differential
\begin{equation*}
    \hbar \divergence_S = - \iota_{\drm S} + \hbar \bv
  \end{equation*}
  on $\PV^{\bullet}(V)$ that we recognize as a deformation of the classical BV differential given by contracting with $\drm S$. Alternatively, we can also write the divergence operator in terms of the Schouten bracket
  % TODO: reference the Schouten bracket form previous lecture
  \begin{equation*}
    \divergence_S = \{ S, \cdot \} + \hbar \bv.
  \end{equation*}
\end{example}

\begin{proposition}[Wick's Lemma]
  We can recover (a baby version of) Wick's Lemma employing just cohomological methods. This lemma gives a formula to compute the moments of the Gaussian measure associated to a free field theory. Let
  \begin{equation*}
    S = \frac{x^2}{2}, \qquad
    \hbar \divergence_S
    = - x \frac{\partial}{\partial \xi}
    + \hbar \frac{\partial}{\partial x} \frac{\partial}{\partial \xi}
  \end{equation*}
  with respect to which we compute
  \begin{align*}
    \divergence_S \bigl( x^{n-1} \xi \bigr)
    &= - x^n + \hbar (n-1) x^{n-2}.
  \end{align*}
  Passing to cohomology we get
  \begin{equation*}
    \bigl[x^n\bigr] = \hbar (n-1) \bigl[x^{n-2}\bigr]
  \end{equation*}
  which we apply recursively to conclude that
  \begin{equation*}
    \bigl[x^n\bigr]
    = \int_V x^n \mu
    = \left\{
      \begin{array}{cl}
        \hbar^{\frac{n}{2}} (n-1)!! & \text{ if } n \in 2 \Zbb_{\geq 0} \\
       0 & \text{ otherwise}
      \end{array}
    \right. .
  \end{equation*}
\end{proposition}

\section{Quantum Master Equation}

The \textbf{quantum master equation} (QME) can be formulated as the requirement that the divergence operator squares to zero
\begin{equation*}
  \divergence_S^2 = 0
\end{equation*}
such that $ \bigl(\PV^{\bullet}, \divergence_S\bigr)$ is a cochain complex.
We have seen that
\begin{equation*}
  \hbar \divergence_S (X)
  = \{ S, X  \} + \hbar \bv (X ),
  \qquad \forall X \in \PV^{-2}(V)
\end{equation*}
therefore
\begin{align*}
  \bigl( \hbar \divergence_S (X) \bigr)^2
    &= \{ S, \{ S, X  \} \}
    + \hbar \{ S, \bv X \} \\
    & \quad + \hbar \bv \{ S, X  \}
    + \hbar^2 \bv^2 X \\
    &= \Bigl\{ \frac{1}{2} \{S, S \} + \hbar \bv S, X  \Bigr\}
\end{align*}
where we employed the graded Jacobi identity for the Schouten bracket
\begin{equation*}
  \{ \{ S, S \}, X  \}
  = 2\{ S, \{ S, X  \} \} 
\end{equation*}
and compatibility with the differential $\bv$
\begin{equation*}
  \bv \{ S, X  \} =
  \{ \bv S, X \} - \{ S, \bv X \}.
\end{equation*}
Because $X$ is arbitrary, we conclude that $\divergence_S^2 = 0$ if
\begin{equation*}
  \frac{1}{2} \{S, S\} + \hbar \bv S = 0.
\end{equation*}
which we recognize as the \textbf{Maurer-Cartan} equation.

We conclude with one more reformulation of the QME. A straightforward but lengthy computation shows that for $X, Y \in \PV^{\bullet}$
\begin{equation*}
  \divergence_S (X \wedge Y)
  = \divergence_S X \wedge Y + (-1)^{|X|} X \divergence_S Y
  + \{ X, Y \}.
\end{equation*}
This is a consequence of the fact that, even though $m_\mu$ defines a chain map, it is not a Lie algebra morphisms with respect to the wedge product.
The failure of $\divergence_S$ to be a derivation is measured by the bracket.
Using this identity, we can formulate the QME as the condition
\begin{equation*}
  \divergence_S \Bigl( \euler^{- \frac{S}{\hbar} } \Bigr) = 0.
\end{equation*}
To see this, note that
\begin{equation*}
  \divergence_S ( \euler^{-\frac{S}{\hbar}} )
  = \Bigl\{ S, \euler^{-\frac{S}{\hbar}} \Bigr\} + \hbar \bv \euler^{-\frac{S}{\hbar}}
  = - \frac{1}{\hbar^2} \Bigl(
  \frac{1}{2} \{ S, S \} + \hbar \bv S \Bigr) \euler^{-\frac{S}{\hbar}}
\end{equation*}
vanishes if
\begin{equation*}
  \frac{1}{2} \{ S, S \} + \bv S = 0.
\end{equation*}
