\chapter{Lecture 12 - Leander Stecker}

% ── Gauge Fixing Operator ─────────────────────────────────────────────
\section{Gauge Fixing Operator}

\begin{definition}
  A free theory in the BV formalism is the data:
  \begin{enumerate}[i)]
    \item a $\Zbb$-graded vector bundle $E \to M$;
    \item a Hermitian nondegenerate pairing $\langle \cdot, \cdot \rangle$ of degree $-1$;
    \item a differential operator $Q \colon \Gamma(E) \to \Gamma(E)$ of degree $1$ such that $Q^2 = 0$ and $Q$ is skew-symmetric with respect to the pairing.
This makes $(E, Q)$ into an elliptic complex.
  \end{enumerate}
\end{definition}

\begin{definition}
  A \textit{gauge fixing operator} $Q^\text{GF} \colon \Gamma(E) \to \Gamma$ is a differential operator of degree $-1$, symmetric with respect to the pairing $\langle \cdot, \cdot \rangle$.
  We define $\Drm = \bigl[Q, Q^\text{GF}\bigr]$, and say that it is a \textit{generalized Laplacian} if
  \begin{equation*}
    \sigma(\Drm)_\xi = - |\xi|^2
  \end{equation*}
  where $|\cdot|$ is defined with respect to any metric on $M$.
\end{definition}

% ── Heat Kernels and Propagators ──────────────────────────────────────
\section{Heat Kernel and Propagators}

\begin{theorem}
  Fix a Hermitian metric $h^i$ on the fibers $E^i$.
  Suppose that $P$ is an elliptic operator, symmetric and positive, that is
  \begin{equation*}
    h^{\Lrm^2}(P s, s) \geq 0, \qquad \forall s \in \Gamma(E).
  \end{equation*}
  Then:
  \begin{enumerate}[i)]
    \item if $u \in \Hrm^\Srm (M, E)$ for Sobolev space, and $P u \in \Crm^\infty (M, E)$, then $u \in \Crm^\infty(E, M)$;
    \item there exists a complex orthonormal basis $\{ u_j \}_{j \in \Zbb_{\geq 0}}$ of $\Lrm^2 (M, E)$ consisting of smooth eigensections of $P$, with eigenvalues
      \begin{equation*}
        0 \geq \lambda_1 \geq \dots \geq \lambda_n \geq \dots
      \end{equation*}
      such that $\lambda_j \in \Crm_j^c$, for some $c = c(n, k) > 0$ depending on $n$ and $k$.
  \end{enumerate}
\end{theorem}

\begin{proof}
  A \textit{rough idea} of the proof is the following. Inverting the symbol gives a pseudo-differential operator that is homogeneous in $\xi^{-k}$.
  Construct an almost-inverse $P^{-1}$ to $P$.
  This operator smooths out functions, implying the first item.
  The second item is a consequence of the spectral theorem for compact operators.
\end{proof}

The operator $\Drm = P P^* + P^* P$ obeys the conditions of the previous theorem.
A generalized Laplacian is, in general, not symmetric nor positive, only at higher order.
However, a generalized Laplacian is of the form
\begin{equation*}
  \Drm^\nabla + \Frm
\end{equation*}
where $\Drm^\nabla$ is symmetric and positive, and $\Frm$ is of order $0$.
